An Efficient Interpolation Technique for Jump Proposals in Reversible-Jump Markov Chain Monte Carlo Calculations

### 2010-12-09 paper.tex
Fixed Eq. 2 reference.

When selecting among alternative models, we are interested in finding the model with the highest evidence $p(M_i|d)$.  However, attempts to directly compute the evidence by performing the integration in Eq.~(\ref{bel}) are generally very difficult in a multi-dimensional, multi-modal parameter space when the likelihood has to be evaluated numerically.  In particular, a grid-based integral quickly becomes computationally unfeasible as the dimensionality of $\vtheta$ exceeds a few.  The parameter space must typically be explored in a stochastic manner before the evidence integral can be computed.  Although several stochastic parameter-exploration techniques are focused directly on evidence computation (e.g., nested sampling and MultiNest \ilya {Add references}), we frequently want to compute the posterior PDFs within each model along with the evidences for the various models, and the Markov chain Monte Carlo is one of the most widely used tools for this purpose.

>>>>

When selecting among alternative models, we are interested in finding the model with the highest evidence $p(M_i|d)$.  However, attempts to directly compute the evidence by performing the integration in Eq.~(\ref{evidence}) are generally very difficult in a multi-dimensional, multi-modal parameter space when the likelihood has to be evaluated numerically.  In particular, a grid-based integral quickly becomes computationally unfeasible as the dimensionality of $\vtheta$ exceeds a few.  The parameter space must typically be explored in a stochastic manner before the evidence integral can be computed.  Although several stochastic parameter-exploration techniques are focused directly on evidence computation (e.g., nested sampling and MultiNest \ilya {Add references}), we frequently want to compute the posterior PDFs within each model along with the evidences for the various models, and the Markov chain Monte Carlo is one of the most widely used tools for this purpose.
